|

### 2021-05-22 article/resubmission.Rmd
methods section

@@

@@

Our survey of the scholarship confirms this continuum of positive,
insignificant, and negative results. Out 
of the `r dim(dat)[1]` coefficients
included in our article sample, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Positive Significant')])`\% of
them are positive and statistically significant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Positive Insignificant')])`\%
are positive and statistically insignificant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Negative Insignificant')])`\%
are negative and statistically insignificant, and `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Negative Significant')])`\% are
negative and statistically significant. A comprehensive survey and systematic review of the existing evidence may help us reach a
meaningful conclusion about the effect of legislature size on public spending.
Meta-analysis is the most appropriate method for this task. Meta-analysis
combines the outcomes of multiple studies into a single estimation and allows
scholars to draw robust conclusions from the aggregated data
[@cooper2019handbook; @hedges1985statistical]. It can also identify potential
sources of study heterogeneity, enabling researchers to assess threats to
external validity and direct future efforts into more promising areas of
academic inquiry [@doucouliagos2008democracy].

@@

We collected the study sample using three criteria. First, the study should
cite \citet{weingast1981political} as their work is foundational to the
distributive politics literature. Second, the study had to use quantitative
methods to estimate the relationship between our variables of
interest.\footnote{As meta-analysis requires a single estimate per observation,
we excluded articles that use interaction terms or quadratic specifications of
our independent variables.} Third, the study should be written in the English
language. We conducted a primary search using Scopus, Microsoft Academic, and
Google Scholar, three large academic databases.\footnote{See the Supplementary
Material for code.} Based on the results obtained, we selected key terms to conduct a broader search of the literature. The same eligibility criteria were applied.

Upon restricting the sample, we identified which were the measurement units most commonly used to translate legislature size and public spending. We found those to be public expenditure as a share of GDP, public expenditure per capita, log public expenditure per capita, lower chamber size, upper chamber size, and log lower chamber size. Log upper chamber size is not a commonly used measurement. Unicameralism is captured by lower chamber size ($n = 7$) and by log lower chamber size ($n = 5$). Since much of the literature dedicated to measuring the effects of bicameralism on this relationship, many articles use both lower and upper chamber sizes as key explanatory variables.

After applying our exclusion criteria, the search produced a dataset of 
`r length(unique(dat$id))` studies as of the 5\textsuperscript{th} of March,
2021. Table \ref{tab:papers} contains the full list of articles from which we
drew data. A PRISMA\footnote{The Preferred Reporting Items for Systematic
Reviews and Meta-Analyses (PRISMA) statement provides a checklist designed
to improve the quality and transparency of study selection processes in
meta-analyses. For more information on the PRISMA framework, see
\citet{liberati2009prisma}.} flow diagram showing the number of resulting
papers after each review step is available in section C.2 of the Supplementary Material.

\footnotesize
\begin{longtable}{>{\raggedright\arraybackslash}p{2.9cm}>{\raggedright\arraybackslash}p{4.5cm}>{\centering\arraybackslash}p{1.3cm}>{\centering\arraybackslash}p{1cm}>{\centering\arraybackslash}p{1cm}>{\centering\arraybackslash}p{1.4cm}>{\centering\arraybackslash}p{2.4cm}}
\caption{Papers included in the meta-analysis, ordered by year of appearance}\\
\toprule
\raggedright Author(s) & \centering Title & \centering Journal & \centering Year & \centering Country & \centering Method & \raggedleft Electoral System
\tabularnewline
\midrule
\endhead
```{r, echo = FALSE, results = 'asis', cache = T}
build_nams <- function(x) {
  x_ <- unlist(strsplit(as.character(x), ' & ', fixed = T, useBytes = T))
  if(length(x_) == 1) return(x_)
  else {
    aux <- x_[1]
      for (i in 2:length(x_))
        if (i == length(x_)){
          aux <- paste(aux, ' \\& \\\\ ', x_[i], sep = '')
        } else {
          aux <- paste(aux, ',\\\\ ', x_[i], sep = '')
        }
  }
  return(paste('\\begin{tabular}[t]{@{}l@{}}', aux,'\\end{tabular}', 
                   sep = ''))
}
aux <- dat %>%
  select(authorCite, title, journalCode, year, locationISO, method, elecsys3) %>%
  unique() %>%
  arrange(year)
for (i in 1:dim(aux)[1]) {
  cat(paste(build_nams(aux$authorCite[i]), ' & ', aux$title[i], ' & ',
      aux$journalCode[i], ' & ', aux$year[i], ' & ', 
      aux$locationISO[i], ' & ', aux$method[i], ' & ', 
      aux$elecsys3[i], ' \\\\ [0.5ex]', sep = ''), '\n')
}
```
\bottomrule
\label{tab:papers}
\begin{minipage}{\textwidth}
\renewcommand{\footnoterule}{}
\vspace{-0.5cm}
\footnotetext{\textbf{Note:} Unpub$=$Unpublished, JPE$=$Journal of Political
Economy, EJPE$=$European Journal of Political Economy, PC$=$Public Choice,
JPubE$=$Journal of Public Economics, JPriE$=$Journal of Private Enterprise,
APSR$=$American Political Science Review, SEJ$=$Southern Economic Journal,
UAR$=$Urban Affairs Review, SCID$=$Studies in Comparative International
Development, SSQ$=$Social Science Quarterly, SPPQ$=$State Politics and Policy
Quarterly, CPS$=$Comparative Political Studies, RivPE$=$Rivista di Politica
Economica, E\&P$=$Economics and Politics, NTJ$=$National Tax Journal.}
\footnotetext{\textbf{Note:} 
OLS$=$Ordinary least squares, IV$=$Instrumental variables, Panel$=$Panel
data/fixed effects, RDD$=$Regression discontinuity design, M$=$Majoritarian,
NM$=$Non-majoritarian (mixed or proportional representation).} 
\footnotetext{\textbf{Note:} Country codes
follow the ISO 3166-1 alpha-3 international standard.} \end{minipage}
\end{longtable}

@@

Our study sample reflects the development of the literature. Although the "law
of $1/n$" was first formulated in 1981, the empirical assessment of the theory
only started a few years later, as dates of publishing range from `r min(dat$year)`
to `r max(dat$year)`. Most studies focus on the United States (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='USA')])`), but our sample also contains
papers on Australia (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='AUS')])`), Brazil (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='BRA')])`), Germany (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='DEU')])`), Indonesia (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='IDN')])`), Italy (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='ITA')])`), and
Switzerland (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='CHE')])`). Five articles use cross-national data and analyse from 2 to 110
countries. Early studies used OLS and panel data methods to estimate the
results, whereas the use of regression discontinuity designs is a recent
addition to the literature, as the first paper to apply it was published in 2012.

Regarding the dependent variables included in the sample, `r as.numeric(table(unique(dat[,c('id','depvar2')])$depvar2)[which(names(table(unique(dat[,c('id','depvar2')])$depvar2))=='ExpPC')])` studies employ
public expenditure per capita, `r as.numeric(table(unique(dat[,c('id','depvar2')])$depvar2)[which(names(table(unique(dat[,c('id','depvar2')])$depvar2))=='logExpPC')])` papers use its natural logarithm, and `r as.numeric(table(unique(dat[,c('id','depvar2')])$depvar2)[which(names(table(unique(dat[,c('id','depvar2')])$depvar2))=='PCTGDP')])` of them
analyse the impact of legislature size on public expenditures as a percentage of
GDP. This indicates that the area has refined the original formulation of $1/n$
suggested by \citet{weingast1981political} and tested the impact of larger
legislatures on different measures of government spending. Our independent
variables of interest are, lower chamber size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='N')])`), the natural
logarithm of lower chamber size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='logN')])`), and upper chamber
size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='K')])`).

We also coded four moderators that may help us understand the heterogeneity in
the reported results. We included them in our meta-regressions alongside an
indicator for the type of independent variable used in the original study (lower chamber size,
log of lower chamber size, or upper chamber
size). The additional moderators are: 1) publication year; 2) paper
publication in an academic journal; 3) electoral system; 4) estimation method.
Since the literature on the "law of $1/n$" is notably diverse, we were
restricted to include only the moderators that either refer to important
theoretical questions, such as the effect of the electoral system on public
spending, or to essential characteristics of the publications themselves.
Although more moderators exist in the literature (ie., data aggregation level),
they do not appear as often as required for the meta-regressions. Table
\ref{tab:descriptive} shows the descriptive statistics of the moderator
variables.

@@

```{r, warning=F, message=F, echo = FALSE, cache=TRUE, results='asis'}
fulldat$usemeta2 <- factor(fulldat$usemeta)
levels(fulldat$usemeta2) <- c("Extended Sample", "Main Sample")
aux <- select(fulldat, usemeta2, indepvar2, elecsys2, method,
              year, published) %>%
  rename(`Independent Variables` = indepvar2,
         `Electoral system`      = elecsys2,
         `Estimation method`     = method,
         `Year`                  = year,
         `Published work`        = published)

export2md(descrTable(~.-usemeta2, aux, y = aux$usemeta2,
                        show.p.overall = F, show.all = T),
          caption = "Descriptive Statistics of Moderators",
          format  = "latex")
```

To ensure we do not violate the effect size independence assumption, we use two strategies.
Since most selected articles submit their data to a number of tests, varying models and controls, each pair of variables has more than one effect size. First, to reduce the impact of multicollinearity within the same article,
we estimate the models using two sets of study coefficients. The first group
includes only the most rigorous model from each paper, that is, those estimated
with the largest $n$, most control variables, and fixed effects if the authors
added them. If the article employed a regression discontinuity design, we chose
the coefficient from the optimal bandwidth or from the intermediate one. This
sample encompasses `r dim(dat)[1]` estimates, as `r as.numeric(sum(table(table(dat$id))[-1]))` articles analysed two dependent or
independent variables of interest \citep{baqir1999districts, bjedov2014impact,
bradbury2001legislative, chen_malhotra_2007, crowley2019law,
lee2016supermajority, lee2018court, maldonado2013legislatures, primo2006stop,
ricciuti2003trading}. Our second sample, in contrast, contains all the `r dim(fulldat)[1]` effect sizes reported in the `r length(unique(dat$id))` papers. Here we focus on the results for our restricted sample as we consider them more robust, but the findings are very similar when we use the extended set. We discuss eventual differences in the next section. There is also dependence between studies when more than one article uses the same dataset or source of evidence. In our study, for instance, several papers used US state and municipal data from the Census Bureau and the Book of the States, for the same constituencies, under the same time period. To override dependence between articles, the second strategy we use is employing a multilevel random effects model, grouping the studies that use overlapping data.

@@

```{r}
#We find a positive effect in our extended
#sample and the coefficient is statistically significant at the 10\% level
#(coefficients = `r mod[[8]]$k`, SMD = `r round(mod[[8]]$TE.random,3)`, SE = `r round(mod[[8]]$seTE.random,3)`, 95\% CI = [`r round(mod[[8]]$lower.random,3)`; `r round(mod[[8]]$upper.random,3)`], $p$-value =
#`r round(mod[[8]]$pval.random,3)`, prediction interval = [`r round(mod[[8]]$lower.predict,3)`; #`r round(mod[[8]]$upper.predict,3)`], $I^2$ = `r round(mod[[8]]$I2*100, 2)`\%). The 
#result supports the "law of 1/$n$", but the evidence is moderate
#as the prediction interval include zero.
```

@@

```{r, echo = FALSE, warning = FALSE, message = FALSE, results = 'hide', cache = TRUE}
res <- list()

## Expenditure as percentage GDP -- Restricted
mod <-  rma(yi = coef,
              sei = SE,
              data = dat,
              method = "REML",
              mods = ~indepvar2+year+published+elecsys2+method,
              test = "knha",
            subset = dat$depvar2=='PCTGDP',
            slab = dat$authoryear)

res[[1]] <- tibble(
     ` ` = c("Intercept",
             "Indepvar: N",
             "Indepvar: logN",
             "Year",
             "Elecsys: Non-Majoritarian",
             "Method: Panel"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4), ")"),
  model = "PCTGDP"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4)))

## Expenditure as percentage GDP -- Extended
mod <- rma(yi = coef,
              sei = SE,
              data = fulldat,
              method = "REML",
              mods = ~ indepvar2+year+published+elecsys2+method,
              test = "knha",
            subset = fulldat$depvar2=='PCTGDP',
            slab = fulldat$authoryear)

res[[2]] <- tibble(
  ` ` = c("Intercept",
          "Indepvar: N",
          "Indepvar: logN",
          "Year",
          "Elecsys: Non-Majoritarian",
          "Method: Panel"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "PCTGDP - All coefs"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))

# Expenditure per capita - Restricted
mod <-  rma(yi = coef,
              sei = SE,
              data = dat,
              method = "REML",
              mods = ~indepvar2+year+published+elecsys2+method,
              test = "knha",
            subset = dat$depvar2=='ExpPC',
            slab = dat$authoryear,
            control=list(maxiter=1000))

res[[3]] <- tibble(
  ` ` = c("Intercept",
          "Indepvar: N",
          "Year",
          "Published: No",
          "Elecsys: Non-Majoritarian",
          "Method: Panel",
          "Method: IV"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "ExpPC"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))

# Expenditure per capita - Extended
mod <- rma(yi = coef,
              sei = SE,
              data = fulldat,
              method = "REML",
              mods = ~ indepvar2+year+published+elecsys2+method,
              test = "knha",
            subset = fulldat$depvar2=='ExpPC',
            slab = fulldat$authoryear)

res[[4]] <- tibble(
  ` ` = c("Intercept",
          "Indepvar: N",
          "Year",
          "Published: No",
          "Elecsys: Non-Majoritarian",
          "Method: Panel",
          "Method: IV"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "ExpPC - All coefs"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))

# Log of Expenditure per capita - Restricted
mod <- rma(yi = coef,
              sei = SE,
              data = dat,
              method = "REML",
              mods = ~indepvar2+year+published+elecsys2+method,
              test = "knha",
            subset = dat$depvar2=='logExpPC',
            slab = dat$authoryear)

res[[5]] <- tibble(
   ` ` = c("Intercept",
           "Indepvar: N",
           "Year",
           "Published: No",
           "Method: Panel"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "logExpPC"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))

# Log of Expenditure per capita - Extended
mod <- rma(yi = coef,
              sei = SE,
              data = fulldat,
              method = "REML",
              mods = ~ indepvar2+year+published+elecsys2+method,
              test = "knha",
            subset = fulldat$depvar2=='logExpPC',
            slab = fulldat$authoryear)

res[[6]] <- tibble(
  ` ` = c("Intercept",
          "Indepvar: N",
          "Year",
          "Published: No",
          "Method: Panel",
          "Method: RDD"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4), ")"),
  model = "logExpPC - All coefs"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))
strep <- function (x) {
  ifelse(x<0.01, '***',ifelse(x<0.05,'**', ifelse(x<0.1,'*','')))
}
```

```{=latex}
\vspace{0.5cm}

\begin{table}[htpb]
\caption{Meta Regression Results\label{tabregressions}}
\footnotesize
\centering
\begin{tabular}{lcccccc}
\toprule
\midrule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Expenditure Per Capita} & \multicolumn{2}{c}{Log Expenditure Per Capita} & \multicolumn{2}{c}{Gov. Spending \% GDP} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){6-7}
& Restricted & Extended & Restricted & Extended & Restricted & Extended \\
\midrule
Independent Variable: $N$ & `r round(res[[3]][2,2],3)` & `r round(res[[4]][2,2],3)` & `r round(res[[5]][2,2],3)` & `r round(res[[6]][2,2],3)` & `r round(res[[1]][2,2],3)` & `r round(res[[2]][2,2],3)`\\
                          & (`r round(res[[3]][2,3],3)`)`r strep(res[[3]][2,5])` & (`r round(res[[4]][2,3],3)`)`r strep(res[[4]][2,5])` & (`r round(res[[5]][2,3],3)`)`r strep(res[[5]][2,5])` & (`r round(res[[6]][2,3],3)`)`r strep(res[[6]][2,5])` & (`r round(res[[1]][2,3],3)`)`r strep(res[[1]][2,5])` & (`r round(res[[2]][2,3],3)`)`r strep(res[[2]][2,5])`\\
%
Independent Variable: log($N$) &  &  &  &  & `r round(res[[1]][3,2],3)` & `r round(res[[2]][3,2],3)`\\
                               &  &  &  &  & (`r round(res[[1]][3,3],3)`)`r strep(res[[1]][3,5])` & (`r round(res[[2]][3,3],3)`)`r strep(res[[2]][3,5])`\\
%
Year & `r round(res[[3]][3,2],3)` & `r round(res[[4]][3,2],3)` & `r round(res[[5]][3,2],3)` & `r round(res[[6]][3,2],3)` & `r round(res[[1]][4,2],3)` & `r round(res[[2]][4,2],3)`\\

>>>>

Agrupamentos possíveis (agrupar só os que batem no nosso resultado): 
- métodos (esse bate)
- institutional design
- electoral system

Introduction:
1 - como está originalmente.
2 - in this letter we run a meta analysis papapá, explicando o que fazemos no texto e o que encontramos.
3 - resultados são all over the place: e a literatura ja sabia que eram all over the place (vira revisãozinha de literatura).
4 - agora a gente diz o que nossos resultados representam pros estudos: no caso, podemos concluir que os autores x, y, z foram pela linha correta.

Results: Colocar resultados da meta-regressão completa na última tabela.

Discussion:
1 - ok
2 - ok, só corrigir
3 - como nossos resultados "resolvem" as questões da teoria
a linha que avalia o desenho institucional está certa dessa forma.
sobre a galera que escreve sobre as dinâmicas internas de competição e coalisão, nós podemos inferir que essas dinâmicas influenciam muito mais do que legislature size.
Juntar a lit review com nosso ultimo paragrafo falando sobre as recomendações de para onde deve avançar a literatura. "Apesar de ela ser extensa, vemos que ainda poderiam ser explorados A B C".
4 - ultimo paragrafo vira o que é o terceiro. uma das sugestões é aumentar o numero de replicações, etc, de como a disciplina como um todo deve avançar, sobre como construimos conhecimento na disciplina.

@@

Colocar aqui no final desse paragrafo "in this paper we..."

@@

Our survey of the scholarship confirms this continuum of positive,
insignificant, and negative results. Out 
of the `r dim(dat)[1]` coefficients
included in our article sample, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Positive Significant')])`\% of
them are positive and statistically significant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Positive Insignificant')])`\%
are positive and statistically insignificant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Negative Insignificant')])`\%
are negative and statistically insignificant, and `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Negative Significant')])`\% are
negative and statistically significant. A comprehensive survey and systematic review of the existing evidence may help us reach a
meaningful conclusion about the effect of legislature size on public spending.

Grudar aqui no final o início do pargrafo seguinte, retirando toda a descrição de ~como conduzimos a meta~, sem descrição das variaveis e modelos.

XXXXXX Meta-analysis is the most appropriate method for this task. Meta-analysis
combines the outcomes of multiple studies into a single estimation and allows
scholars to draw robust conclusions from the aggregated data
[@cooper2019handbook; @hedges1985statistical]. It can also identify potential
sources of study heterogeneity, enabling researchers to assess threats to
external validity and direct future efforts into more promising areas of
academic inquiry [@doucouliagos2008democracy]. XXXXXXXX

@@

We compiled our final sample of papers from two large collections of records. In the first round of the search, we scraped three large academic databases (Scopus, Microsoft Academic, and Google Scholar) for studies that cited \citet{weingast1981political}. We developed exclusion criteria to select only articles written in the English language that used quantitative methods to investigate the relationship between legislature size and public spending.\footnote{Please refer to section C in the Supplementary Material for a more detailed description of the selection procedure, including a PRISMA (Preferred Reporting Items for Systematic Reviews and Meta-Analyses) flow diagram \citet{liberati2009prisma} showing the number of resulting papers after each review step.} Upon restricting the sample, we identified which were the most commonly used measurements to operationalise these variables of interest, and adopted them as our key explanatory variables.\footnote{As meta-analysis requires a single estimate per observation, we excluded articles that use interaction terms or quadratic specifications of our independent variables.} We found those to be public expenditure as a share of GDP, public expenditure per capita, and the natural logarithm of public expenditure per capita as dependent variables. As independent variables, most studies use lower chamber size, upper chamber size, and the natural logarithm of lower chamber size.\footnote{There are a few important nuances to the coding of these variables. Unicameralism is captured by lower chamber size ($n = 7$) and by log lower chamber size ($n = 5$). Since much of the literature estimates how institutional designs affect this relationship, ours and many other articles use both lower and upper chamber sizes as key explanatory variables. We did not find any articles that used the natural logarithm of upper chamber size.} In the second round, we selected key terms to conduct a broader search of the literature on Google Scholar and applied the same eligibility criteria. Combined, the two searches produced a dataset of `r length(unique(dat$id))` studies as of the 10\textsuperscript{th} of March, 2021. Table \ref{tab:papers} contains the full list of articles from which we drew data.

\footnotesize
\begin{longtable}{>{\raggedright\arraybackslash}p{3.9cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2.3cm}>{\centering\arraybackslash}p{1cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{1cm}}
\caption{Papers included in the meta-analysis, ordered by year of appearance}\\
\toprule
\raggedright Author(s) & \centering Journal & \centering Country & \centering Dependent Variable & \centering Method & \centering Institutional Design & \centering Electoral System
\tabularnewline
\midrule
\endhead 
```{r papers, echo = FALSE, results = 'asis', cache = T}
build_nams <- function(x) {
  x_ <- unlist(strsplit(as.character(x), ' & ', fixed = T, useBytes = T))
  if(length(x_) == 1) return(x_)
  else {
    aux <- x_[1]
      for (i in 2:length(x_))
        if (i == length(x_)){
          aux <- paste(aux, ' \\& \\\\ ', x_[i], sep = '')
        } else {
          aux <- paste(aux, ',\\\\ ', x_[i], sep = '')
        }
  }
  return(paste('\\begin{tabular}[t]{@{}l@{}}', aux,'\\end{tabular}', 
                   sep = ''))
}
aux <- dat %>%
  select(authoryear, journalCode, locationISO, depvar2, method, instdesign, elecsys3, year) %>%
  unique() %>%
  arrange(year)
for (i in 1:dim(aux)[1]) {
  cat(paste(build_nams(aux$authoryear[i]), ' & ', aux$journalCode[i], ' & ',
      aux$locationISO[i], ' & ', aux$depvar2[i], ' & ', 
      aux$method[i], ' & ', aux$instdesign[i], ' & ', 
      aux$elecsys3[i], ' \\\\ [0.5ex]', sep = ''), '\n')
}
```
\bottomrule
\label{tab:papers}
\begin{minipage}{\textwidth}
\renewcommand{\footnoterule}{}
\vspace{-0.5cm}
\footnotetext{\textbf{Note:} Unpub$=$Unpublished, JPE$=$Journal of Political
Economy, EJPE$=$European Journal of Political Economy, PC$=$Public Choice,
JPubE$=$Journal of Public Economics, JPriE$=$Journal of Private Enterprise,
APSR$=$American Political Science Review, SEJ$=$Southern Economic Journal,
UAR$=$Urban Affairs Review, SCID$=$Studies in Comparative International
Development, SSQ$=$Social Science Quarterly, SPPQ$=$State Politics and Policy
Quarterly, CPS$=$Comparative Political Studies, RivPE$=$Rivista di Politica
Economica, E\&P$=$Economics and Politics, NTJ$=$National Tax Journal.}
\footnotetext{\textbf{Note:} 
OLS$=$Ordinary least squares, IV$=$Instrumental variables, Panel$=$Panel
data/fixed effects, RDD$=$Regression discontinuity design, M$=$Majoritarian,
NM$=$Non-majoritarian (mixed or proportional representation).} 
\footnotetext{\textbf{Note:} Country codes
follow the ISO 3166-1 alpha-3 international standard.}
\footnotetext{\textbf{Note:} ExpPC$=$Per capita expenditure, logExpPC$=$Natural logarithm of per capita expenditure, PCTGDP$=$Expenditure as a percentage of GDP.}\end{minipage}
\end{longtable}

@@

Our study sample reflects the development of the literature. Although the "law
of $1/n$" was first formulated in 1981, the empirical assessment of the theory
only started a few years later, as dates of publishing range from `r min(dat$year)`
to `r max(dat$year)`. Most studies focus on the United States (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='USA')])`), but our sample also contains
papers on Australia (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='AUS')])`), Brazil (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='BRA')])`), Germany (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='DEU')])`), Indonesia (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='IDN')])`), Italy (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='ITA')])`), and
Switzerland (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='CHE')])`). Eight articles use cross-national data and analyse from 2 to 110
countries. Early studies used OLS and panel data methods to estimate the
results, whereas the use of regression discontinuity designs is a recent
addition to the literature, as the first paper to apply it was published in 2012.

Regarding the dependent variables included in the sample, `r as.numeric(table(unique(dat[,c('id','depvar2')])$depvar2)[which(names(table(unique(dat[,c('id','depvar2')])$depvar2))=='ExpPC')])` studies employ
public expenditure per capita, `r as.numeric(table(unique(dat[,c('id','depvar2')])$depvar2)[which(names(table(unique(dat[,c('id','depvar2')])$depvar2))=='logExpPC')])` papers use its natural logarithm, and `r as.numeric(table(unique(dat[,c('id','depvar2')])$depvar2)[which(names(table(unique(dat[,c('id','depvar2')])$depvar2))=='PCTGDP')])` of them
analyse the impact of legislature size on public expenditures as a percentage of
GDP. This indicates that the area has refined the original formulation of $1/n$
suggested by \citet{weingast1981political} and tested the impact of larger
legislatures on different measures of government spending. Our independent
variables of interest are lower chamber size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='N')])`), the natural
logarithm of lower chamber size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='logN')])`), and upper chamber
size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='K')])`).

We also coded five moderators that may help us understand the heterogeneity in
the reported results. We included them in our meta-regressions alongside an
indicator for the type of independent variable used in the original study. The additional moderators are: 1) publication year; 2) paper
publication in an academic journal; 3) estimation method; 4) institutional design; 5) electoral system.
Since the literature on the "law of $1/n$" is notably diverse, we included only moderators that either refer to important
theoretical questions, such as the effect of the electoral system on public
spending, or to essential characteristics of the publications themselves.
Although more moderators exist in the literature (ie., data aggregation level),
they do not appear as often as required for the meta-regressions. Table
\ref{tab:descriptive} shows the descriptive statistics of the moderator
variables.

@@

\footnotesize
```{r descriptive, warning=F, message=F, echo = FALSE, cache=TRUE, results='asis'}
fulldat$usemeta2 <- factor(fulldat$usemeta)
levels(fulldat$usemeta2) <- c("Other Coefficients", "Main Sample")
aux <- select(fulldat, usemeta2, indepvar2, elecsys2, method,
              year, published, instdesign) %>%
  rename(`Independent Variables` = indepvar2,
         `Year`                  = year,
         `Published work`        = published,
         `Estimation method`     = method,
         `Institutional Design`  = instdesign,
         `Electoral system`      = elecsys2)

export2md(descrTable(~.-usemeta2, aux, y = aux$usemeta2,
                        show.p.overall = F, show.all = T),
          caption = "Descriptive Statistics of Moderators",
          format  = "latex")
```
\normalsize

One of the assumptions in meta-analyses is effect size independence. In our sample of coefficients, we have sources of independence within and between articles, and we solve them using two distinct procedures. Since authors often submit their data to different models, each paper reports several effect sizes using the same variables. To reduce the impact of multicollinearity,
we produce and analyse two sets of study coefficients. The first group
includes only the most rigorous model from each paper, that is, those estimated
with the largest $n$, most control variables, and fixed effects if the authors
added them. If the article employed a regression discontinuity design, we chose
the coefficient from the optimal bandwidth or from the intermediate one. This
sample encompasses `r dim(dat)[1]` estimates, as `r as.numeric(sum(table(table(dat$id))[-1]))` articles analysed two dependent or
independent variables of interest \footnote{The papers that used more than one dependent or independent variable of interest were \citet{baqir1999districts, bjedov2014impact,
bradbury2001legislative, chen2007law, crowley2019law, erler2007termlimits, gilligan2001fiscal, lee2016supermajority, lee2018court, maldonado2013legislatures, primo2006stop, ricciuti2003trading, ricciuti2004legislatures}.}. Our second sample, in contrast, contains all the `r dim(fulldat)[1]` effect sizes reported in the `r length(unique(dat$id))` papers. In both restricted and extended sets, a number of papers use overlapping data -- from the same constituency, using the same variables, during the same time period.\footnote{For instance, 8 papers used U.S. State data from both the U.S. Census Bureau’s “Annual Survey of State and Local Government Finances” and The Council of State Government’s Book of the
States.} We correct this source of bias by employing a multilevel random effects model [@cheung2014modeling], grouping redundant(?) studies. Here we focus on the results for our restricted sample as we consider them more robust, but the findings are very similar when we use the extended set. We discuss eventual differences in the next section.

@@

XXXXX We find a positive effect in our extended
sample and the coefficient is statistically significant at the 10\% level
(coefficients = `r mod[[8]]$k`, SMD = `r round(mod[[8]]$TE.random,3)`, SE = `r round(mod[[8]]$seTE.random,3)`, 95\% CI = [`r round(mod[[8]]$lower.random,3)`; `r round(mod[[8]]$upper.random,3)`], $p$-value =
`r round(mod[[8]]$pval.random,3)`, prediction interval = [`r round(mod[[8]]$lower.predict,3)`; #`r round(mod[[8]]$upper.predict,3)`], $I^2$ = `r round(mod[[8]]$I2*100, 2)`\%). The 
result supports the "law of 1/$n$", but the evidence is moderate
as the prediction interval include zero. XXXXXXXXX

@@
